A studyforrest extension, an annotation of spoken language in the German dubbed movie ``Forrest Gump'' and its audio-description

### 2020-05-20 paper/main.tex
revise abstract

\todo{Wort zur Validierungsstudie; Es sind erst 110 von max 300 Worten verbraucht; Werte würde ich eher runden }
\thispagestyle{fancy}
\begin{abstract}
% up to 300 words
Here we present an annotation of speech in the audio-visual movie ``Forrest Gump'' and its audio-description (i.e. the audio-only variant) as an addition to a large public functional brain imaging dataset (\href{www.studyforrest.org}{studyforrest.org}).
The annotation provides information about the exact timing of each of the \aSentencesAll\ spoken sentences, \aWordsAll\ words (including \aPosNonspeechAll\ non-speech vocalizations), \aPhonesAll\ phonemes and its corresponding speaker.
Additionally for every word, we provide lemmatization, two different part-of-speech taggings (simple and detailed), syntactic dependencis within each sentence, and a 300-dimensional semantic representation (word vector).
This annotation facilitates further studies of language perception and semantic processing under conditions of real-life complexity using the \textit{studyforrest} dataset.
\todo[inline]{I don't understand what "two different part-of-speech taggings (simple and detailed)" means}
\todo[inline]{"300-dimensional semantic representation (word vector)" I think we need to find a better description, but I could not come up with one so far}
\end{abstract}

>>>>

\todo{Wort zur Validierungsstudie; Es sind erst 110 von max 300 Worten verbraucht; Werte würde ich eher runden }
\thispagestyle{fancy}
\begin{abstract}
% up to 300 words
Here we present an annotation of speech in the audio-visual movie ``Forrest Gump'' and its audio-description (i.e. the audio-only variant) as an addition to a large public functional brain imaging dataset (\href{www.studyforrest.org}{studyforrest.org}).
The annotation provides information about the exact timing of each of the \aSentencesAll\ spoken sentences, \aWordsAll\ words (including \aPosNonspeechAll\ non-speech vocalizations), \aPhonesAll\ phonemes and its corresponding speaker.
Additionally for every word, we provide lemmatization, a simple
part-of-speech-tagging putting words into 15 grammatical categories, a detailed
part-of-speech tagging putting words into 43 grammatical categories, syntactic
dependencies within each sentence, and a semantic analysis based on word
embedding providing a 300-dimensional word vector.
This annotation facilitates further studies of language perception and semantic processing under conditions of real-life complexity using the \textit{studyforrest} dataset.
\end{abstract}
